Case study validations of automatic bullet matching

### 2018-11-13 index.Rmd
Transitional paragraph, changes in headings for consistency, and other tweaks

\svp{The random forest presented in \citet{aoas} takes as input the following characteristics derived from a pair of aligned sequences:
\begin{itemize}
\item Cross-correlation 
\item Number of matching striae 
\item Total depth of joint striations 
\item Number of non-matching striae 
\item Euclidian distance between the sequences 
\item Consecutive Matching Striae 
\item Consecutive Non-matching Striae
\end{itemize}

The output of the random forest is a score between 0 and 1 representing the algorithm's assessment of the strength of the match, where 1 indicates that the algorithm believes it to be highly likely that the aligned signatures match, and 0 indicates that the aligned signatures are highly likely to originate from different lands.}

# Assessing Match Strength
\svp{Each of the features described in the previous section, as well as the random forest score, describe comparisons on a land-to-land basis. While these comparisons are useful, it is typically more useful to assess the entire physical object (e.g. all lands on a single bullet) to describe the correspondance between two pieces of physical evidence. In order to aggregate land-to-land match scores, we must consider the physical structure of the evidence; that is, that the sequence of lands stems from spatial information, but the numbering of each land represents the scan order and start point rather than encoding useful information. }

## Sequence Average Maximum

@@

@@

@@

>>>>

\svp{The random forest presented in \citet{aoas} takes as input the following characteristics derived from a pair of aligned sequences:}
\svp{\begin{itemize}
\item Cross-correlation 
\item Number of matching striae 
\item Total depth of joint striations 
\item Number of non-matching striae 
\item Euclidian distance between the sequences 
\item Consecutive Matching Striae 
\item Consecutive Non-matching Striae
\end{itemize}}
\svp{The output of the random forest is a score between 0 and 1 representing the algorithm's assessment of the strength of the match, where 1 indicates that the algorithm believes it to be highly likely that the aligned signatures match, and 0 indicates that the aligned signatures are highly likely to originate from different lands.}

# Assessing Match Strength
\svp{Each of the features described in the previous section, as well as the random forest score, describe comparisons on a land-to-land basis. While these comparisons are useful, it is typically more useful to assess the entire physical object (e.g. all lands on a single bullet) to describe the correspondance between two pieces of physical evidence.}
<!-- \svp{In order to aggregate land-to-land match scores, we must consider the physical structure of the evidence; that is, that the sequence of lands stems from spatial information, but the numbering of each land represents the scan order and start point rather than encoding useful information. } --><!--This last bit might be redundant-->

@@

## Land-to-Land Comparisons

@@

## Bullet-to-Bullet Comparisons

@@

\svp{In this paper, we validate the algorithm described in \citet{aoas} on three external test sets. We assess the results on each set and evaluate whether the minimal requirements described above are fulfilled. We compare the random forest algorithm's performance to the performance of other suggested measures for quantitative assessment of match strength, such as cross-correlation and consecutive matching striae.}
